---
title: "Project3 README"
author: "Ruben Sowah, Zhiyuan Yang"  
date: "2022-11-14"
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F, cache = T)
```

# Purpose of the repository

  This repository is created to complete the third project of a data science class (ST558). The goal of this project is to read in an [online news popularity data set](https://archive.ics.uci.edu/ml/datasets/Online+News+Popularity), perform variable selections, split the data into a train and test sets, fit some machine learning models(linear regression, random forest, boosted tree models) on the train set, predict the number of shares of the articles on the test set, and see which model performs the best. The comparison of the models as well as the whole project are automated  across six different channels.


# List of R Packages used 

  The following packages are used in completing the project
  
```{r, eval = F}  
tidyverse  
caret  
Metrics  
ggplot2  
readr 
tibble
rsample  
randomForest  
rmarkdown  
```


# README render code
```{r render, echo=TRUE, eval=F}
rmarkdown::render("Project3_README.Rmd", 
          output_format = "github_document",
          output_file = "README.md",
          output_options = list(
            html_preview = FALSE))
```

# Links to the generated analyses:   

* [Entertainment channel analysis](data_channel_is_entertainment.md).  
* [Lifestyle channel analysis](data_channel_is_lifestyle.md). 
* [Business channel analysis](data_channel_is_bus.md). 
* [Social media channel analysis](data_channel_is_socmed.md). 
* [Technology channel analysis](data_channel_is_tech.md). 
* [World channel analysis](data_channel_is_world.md). 


# Code used to create the analyses

  * __Set up parameters for the automation code, print the reports__
```{r, echo = T , eval = T}
channels <- c("data_channel_is_lifestyle", "data_channel_is_entertainment", "data_channel_is_bus", "data_channel_is_socmed", "data_channel_is_tech", "data_channel_is_world")

## Files
output_file <- paste0(channels,".md")

## Create a list for each channel with just channel name parameter
 params = lapply(channels, FUN = function(x){
 
   return(list(chan = x))

})
## Put into a tibble
reports = tibble(channels, output_file, params);reports
```

  * __Automation of the code__
```{r, eval=F}
## Automation
apply(reports, MARGIN = 1, FUN = function(x){

  rmarkdown::render(input = "Project3.Rmd",

                    output_format = "github_document",

                    output_file = x[[2]],

                    params = x[[3]],

                    output_options = list(html_preview = FALSE))

})
```


  