---
title: "Project3 README"
author: "Ruben Sowah, Zhiyuan Yang"
date: "2022-11-14"
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F, cache = T)
library(dplyr)
library(knitr)
```


# README code
```{r render, echo=TRUE, eval=F}
rmarkdown::render("Project3_README.Rmd", 
          output_format = "github_document",
          output_file = "README.md",
          output_options = list(
            html_preview = FALSE))
```

# Automation code
```{r, echo = T , eval = T}
channels <- c("data_channel_is_lifestyle", "data_channel_is_entertainment", "data_channel_is_bus", "data_channel_is_socmed", "data_channel_is_tech", "data_channel_is_world")

## Files
output_file <- paste0(channels,".md")

## Create a list for each channel with just channel name parameter
 params = lapply(channels, FUN = function(x){
 
   return(list(chan = x))

})
## Put into a data frame
reports = tibble(channels, output_file, params);reports
```

```{r, eval=F}
## Automation

apply(reports, MARGIN = 1, FUN = function(x){

  rmarkdown::render(input = "Project3.Rmd",

                    output_format = "github_document",

                    output_file = x[[2]],

                    params = x[[3]],

                    output_options = list(html_preview = FALSE))

})
```

# Reports  for each channel:   

* [Entertainment channel analysis](Project3.md).  
* [Lifestyle channel analysis](data_channel_is_lifestyle.md). 
* [Business channel analysis](data_channel_is_bus.md). 
* [Social media channel analysis](data_channel_is_socmed.md). 
* [Technology channel analysis](data_channel_is_tech.md). 
* [World channel analysis](data_channel_is_world.md). 
  